On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-08-27 paper.tex
Minor fixes

 \item Case $\alpha\perp\alpha'$. As before, we may assume $\alpha'=\gamma$.
\begin{align*}
{}^{S_\gamma(t^d)}S_\alpha(bt^{m+1}) = {}^{S_\gamma(t^d)}[x_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] & \text{ by~\cref{lem:bmp1}}\\
 = [S_{-\beta}(b't^{m+1}), {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]                                     & \text{ by Case~\eqref{case:2a} since $\gamma\not\perp-\beta$}\\
 = [[x_{-\beta-\gamma}(b''t^{m+1-d}), S_\gamma(t^d)], {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]          & \text{ by~\eqref{eq:verify-bmp1'}}\\
 = [x_{-\beta-\gamma}(b''t^{m+1-d)}), [S_\gamma(t^d), x_{\alpha+\beta}(1)]]                           & \text{ by~\eqref{eq:H1iii} and~\eqref{eq:bm} since $m+1-d \leq m$}\\
 = S_{\alpha}(b'''t^{m+1})                                                                            & \text{ by $(c_m)$ and \eqref{eq:verify-bmp1'}} \end{align*}
 Usual identities for structure constants imply (cf.~\cite[p.~12]{Re75}):
 \[b'''=N_{-\beta-\gamma, \alpha+\beta+\gamma} \cdot N_{\gamma, \alpha+\beta} \cdot N_{-\beta-\gamma, \gamma} \cdot N_{-\beta, \alpha+\beta} \cdot b = b, \] 
\end{enumerate}
This finishes the proof of~\eqref{eq:verify-bmp2} in the special case $a=1$.
\item Now we deduce~\eqref{eq:verify-bmp2} for arbitrary $\xi = at^d$, $a\in A$ and $1\leq d\leq m+1$. Again, there are two subcases.
\begin{enumerate}
\item \label{case:3a} Case $\alpha \not\perp \alpha'$. % not possible to induct on k here :(
 \begin{align*} 
 [S_\alpha(at^d), S_{\alpha + \beta}(bt^{m+1})] = 
 [S_\alpha(at^d), [S_{\alpha+\beta+\gamma}(t^{m+1}), x_{-\gamma}(b')]] & \text{ by~\cref{lem:bmp1}} \\
  = [[x_\alpha(at^d), S_{\alpha+\beta+\gamma}(t^{m+1})], {}^{S_{\alpha+\beta+\gamma}(t^{m+1})}\!x_{-\gamma}(b')] & \text{ by $(b_k)$ or Case~\eqref{case:1} if $k=m+1$} \\
  = 1 & \text{ by Case~\eqref{case:2}.} \end{align*}
\item Case $\alpha \perp \alpha'$.
\begin{align*}
 S_{\alpha+\beta+\gamma}(abt^{m+1}) = {}^{S_{-\beta}(t^d)}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) & \text{ by Case~\eqref{case:2}}\\
 = {}^{S_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] & \text{ by~\eqref{eq:verify-bmp1'}} \\
 = [S_{\alpha}(b't^{m+1}) x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] & \text{ by~\eqref{eq:verify-bmp1'} and $(b_d)$ if $d\leq m$ or Case~\eqref{case:2} if $d=m+1$ }\\
 = {}^{S_{\alpha}(b't^{m+1})}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] & \text{ by~\eqref{eq:H1ii} and~\eqref{eq:verify-bmp1'}} \\
 = S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] & \text{ by Case~\eqref{case:3a},}
\end{align*}
from which the required identity follows. \qedhere
\end{enumerate}
\end{enumerate}
\end{proof}

>>>>

 \item Case $\alpha\perp\alpha'$. As before, we may assume $\alpha'=\gamma$.
\begin{align*}
{}^{S_\gamma(t^d)}S_\alpha(bt^{m+1}) = {}^{S_\gamma(t^d)}[S_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] & \text{ by~\cref{lem:bmp1}}\\
 = [S_{-\beta}(b't^{m+1}), {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]                                     & \text{ by Case~\eqref{case:2a} since $\gamma\not\perp-\beta$}\\
 = [[x_{-\beta-\gamma}(b''t^{m+1-d}), S_\gamma(t^d)], {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]          & \text{ by~\eqref{eq:verify-bmp1'}}\\
 = [x_{-\beta-\gamma}(b''t^{m+1-d)}), [S_\gamma(t^d), x_{\alpha+\beta}(1)]]                           & \text{ by~\eqref{eq:H1iii} and~\eqref{eq:bm} since $m+1-d \leq m$}\\
 = S_{\alpha}(b'''t^{m+1})                                                                            & \text{ by~\eqref{eq:verify-bmp1'}} \end{align*}
 Usual identities for structure constants imply (cf.~\cite[p.~12]{Re75}):
 \[b'''=N_{-\beta-\gamma, \alpha+\beta+\gamma} \cdot N_{\gamma, \alpha+\beta} \cdot N_{-\beta-\gamma, \gamma} \cdot N_{-\beta, \alpha+\beta} \cdot b = b, \] 
\end{enumerate}
This finishes the proof of~\eqref{eq:verify-bmp2} in the special case $a=1$.
\item Now we deduce~\eqref{eq:verify-bmp2} for arbitrary $\xi = at^d$, $a\in A$ and $1\leq d\leq m+1$. Again, there are two subcases.
\begin{enumerate}
\item \label{case:3a} Case $\alpha \not\perp \alpha'$. % not possible to induct on k here :(
 \begin{align*} 
 [S_\alpha(at^d), S_{\alpha + \beta}(bt^{m+1})] = 
 [S_\alpha(at^d), [S_{\alpha+\beta+\gamma}(t^{m+1}), x_{-\gamma}(b')]] & \text{ by~\cref{lem:bmp1}} \\
  = [[x_\alpha(at^d), S_{\alpha+\beta+\gamma}(t^{m+1})], {}^{S_{\alpha+\beta+\gamma}(t^{m+1})}\!x_{-\gamma}(b')] & \text{ by $(b_k)$ or Case~\eqref{case:1} if $k=m+1$} \\
  = 1 & \text{ by Case~\eqref{case:2}.} \end{align*}
\item Case $\alpha \perp \alpha'$.
\begin{align*}
 S_{\alpha+\beta+\gamma}(abt^{m+1}) = {}^{S_{-\beta}(t^d)}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) & \text{ by Case~\eqref{case:2}}\\
 = {}^{S_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] & \text{ by~\eqref{eq:verify-bmp1'}} \\
 = [S_{\alpha}(b't^{m+1}) x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] & \text{ by~\eqref{eq:verify-bmp1'} and $(b_d)$ if $d\leq m$ or Case~\eqref{case:2} if $d=m+1$ }\\
 = {}^{S_{\alpha}(b't^{m+1})}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] & \text{ by~\eqref{eq:H1ii} and~\eqref{eq:verify-bmp1'}} \\
 = S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] & \text{ by Case~\eqref{case:3a},}
\end{align*}
from which the required identity follows. \qedhere
\end{enumerate}
\end{enumerate}
\end{proof}
